---
title: ""
date: '`r format(Sys.Date())`'
author:
  - James R. Junker:
      email: james.junker@unt.edu
      institute: [unt, aeri]
      correspondence: true
  - name: Jeff S. Wesner
    institute: usd
  - name: Justin Pomeranz
    institute: cmu
  - name: Vojsava Gjoni
    institute: ital
institute:
  - unt: Dept. of Biological Sciences, University of North Texas, Denton, TX USA
  - aeri: Advanced Environmental Research Institute, University of North Texas, Denton, TX USA
output:
  word_document:
    reference_docx: working_docx_template.docx
    toc: no
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
      - '--filter=pandoc-crossref.exe'
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \usepackage{indentfirst}
- \usepackage{nicefrac}
- \numberwithin{equation}
- \linenumbers
indent: true
linestretch: 1
bibliography: supp_refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

```{r init, echo = FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
here::i_am("doc/ISD-CCSR_ms.Rmd")
```

## Purpose

Start the initial analysis combining ISD, CCSR, and LSD relationships across the NEON sites. This is initial fodder for discussion of next steps.

## Introduction

The negative relationship between abundance and body size is one of the most widely observed ecological patterns []. This relationships manifests across biological levels of organization from individuals within a species to whole food webs [@white2007]...


```{r load data, warning = FALSE}
library(ggeffects)
# library(marginaleffects)
library(latex2exp)
library(here)
library(junkR)
library(vegan)
library(tidyverse)
library(tidybayes)
library(cowplot)
library(ggdist)
library(modelr)
library(rstan)
library(brms)
library(viridis)
library(mgcv)
library(hillR)
library(MASS)

theme_set(theme_minimal(base_family = 'serif'))

options(mc.cores = parallel::detectCores(),
        scipen = 5)
rstan::rstan_options(auto_write = TRUE)
source(here::here("R/helpers.R"))

# these sites are outliers in that they don't contain fish
# removing them here to compare apples to apples
# filter outliers sites from all the exported objects first
outlier_sites = c('CARI','OKSR')

# read in the data for species richness across sites
coords = read.csv(here('data/classified_coordinates.csv')) %>% filter(!duplicated(.)) %>% 
  rename(site_id = 'siteID') %>%
  #filter outlier sites
  filter(site_id %ni% outlier_sites)

taxa_list = readRDS(here('data/taxa_list.rds'))
H_dat = readRDS(here('data/macro_fish_diversity.rds'))%>%
  #filter outlier sites
  filter(site_id %ni% outlier_sites)

H_summ = H_dat %>% 
  summarise(S_obs_inc = mean(Species),
            S_chao_inc = mean(chao),
            S_jack1_inc = mean(jack1),
            S_jack2_inc = mean(jack2),
            S_boot_inc = mean(boot),
            S_obs_rar = mean(S.obs),
            S_chao1_rar = mean(S.chao1),
            S_ACE_rar = mean(S.ACE, na.rm = TRUE),
            hill_0 = mean(hill_0),
            hill_1 = mean(hill_1),
            hill_2 = mean(hill_2),
            .by = c('site_id')
            ) %>% 
  mutate(across(where(is.numeric), round)) %>% 
  mutate(across(contains('hill'), ~log(.x), .names = "L{.col}")) %>% 
  left_join(coords, by = 'site_id')

# read in data and calc sample level summaries
# dw_dat = readRDS(here("data/))
# dw_dat = readRDS(here("data/dat_2022_notculled.rds")) %>% 
dw_dat = readRDS(here('data/dat_2022_clauset.rds')) %>% 
  ungroup %>% 
  #filter outlier sites
  filter(site_id %ni% outlier_sites) %>% 
  #clean to relevant columns for sample summaries
  dplyr::select(dw, no_m2, site_id, collect_date, sample_id, log_gpp_s, log_om_s, mat_s) %>% 
  mutate(collect_date = as.Date(collect_date),
         year = year(collect_date),
         month = month(collect_date),
         year_month = paste(year, month, sep = "_"),
         n_sum = sum(no_m2),
         n_rel = no_m2/n_sum,
         b_m2 = no_m2*dw,
         b_sum = sum(b_m2),
         b_rel = b_m2/b_sum,
         .by = c('site_id', 'sample_id'))

# get weighted mean body size
dw_dat_temp = dw_dat %>% 
  ungroup %>% 
  mutate(dw_met = dw^0.75) %>%
  summarise(n_tot = unique(n_sum),
            ln_tot = log(n_tot),
            mbar_n_met = weighted.mean(dw_met, w = n_rel),
            mbar_b_met = weighted.mean(dw_met, w = b_rel),
            mbar_n = weighted.mean(dw, w = n_rel),
            mbar_b = weighted.mean(dw, w = b_rel),
            lmbar_n_met = log(mbar_n_met),
            lmbar_b_met = log(mbar_b_met),
            lmbar_n = log(mbar_n),
            lmbar_b = log(mbar_b),
            b_m2 = unique(b_sum),
            lb_m2 = log(b_m2),
            m_max = max(dw, na.rm = TRUE),
            .by = c('site_id','sample_id')) %>% 
  mutate(across(all_of(c("ln_tot", "lmbar_n_met", "lmbar_b_met", "lmbar_n", "lmbar_b")), ~as.numeric(scale(.)), .names  = "{.col}_s")) %>% 
  left_join(dw_dat %>% ungroup %>% dplyr::select(site_id, log_gpp_s, log_om_s, mat_s) %>% distinct(), by = 'site_id')

# read in lambdas by sample_id
lambdas = readRDS(here("data/lambda_table.rds")) %>% 
  dplyr::select(sample_id, lambda_med = lambda_median, lower_lambda = '.lower', upper_lambda = '.upper') %>% 
  left_join(readRDS(here('data/dat_2022_notculled.rds'))%>%
              #filter outlier sites
              filter(site_id %ni% outlier_sites) %>% 
              dplyr::select(site_id, collect_date, sample_id) %>%
              distinct() %>% 
              mutate(collect_date = as.Date(collect_date),
                     year = year(collect_date),
                     month = month(collect_date),
                     year_month = paste(year, month, sep = "_")
                     ), by = 'sample_id'
            ) %>% 
  dplyr::select(site_id, sample_id, lambda_med, lower_lambda, upper_lambda) %>% 
  distinct()

dw_dat_summ = merge(dw_dat_temp, lambdas,  by = c('site_id','sample_id'), all = TRUE) %>% 
  left_join(H_summ, by = 'site_id')

sampleParams <- readRDS(here("data/dat_2022_clauset.rds")) %>%
  ungroup %>%
  # filter outliers sites from all the exported objects first
  filter(site_id %ni% outlier_sites) %>% 
  dplyr::select(site_id, sample_id, year, xmin_c = xmin_clauset, xmax) %>%
  distinct %>% 
  left_join(dw_dat_summ, by = c('sample_id', 'site_id')) 

dat = sampleParams %>% 
  # lambda = ..24
  # xmin = ..4
  # xmax = ..5
  # n_tot = ..6
  filter(xmin_c < 1.5,
         lambda_med > -2.5) %>% 
    mutate(m_old = pmap_dbl(.,~pareto_expectation(lambda = ..27,
                                                  xmin = ..4,
                                                  xmax = ..5)),
           lmbar_n_est = pmap_dbl(.,~log(pareto_expectation(lambda = ..27,
                                                  xmin = 0.006,
                                                  xmax = ..5))),
           lmbar_n_est_l = pmap_dbl(.,~log(pareto_expectation(lambda = ..28,
                                                    xmin = 0.006,
                                                    xmax = ..5))),
           lmbar_n_est_u = pmap_dbl(.,~log(pareto_expectation(lambda = ..29,
                                                    xmin = 0.006,
                                                    xmax = ..5))),
           lmbar_b_est = pmap_dbl(., ~log(pareto_expectation(lambda = (..27 + 1),
                                                             xmin = 0.006,
                                                             xmax = ..5))),
           lmbar_b_est_l = pmap_dbl(., ~log(pareto_expectation(lambda = (..28 + 1),
                                                               xmin = 0.006,
                                                               xmax = ..5))),
           lmbar_b_est_u = pmap_dbl(., ~log(pareto_expectation(lambda = (..29 + 1),
                                                               xmin = 0.006,
                                                               xmax = ..5))),
           n_est = pmap_dbl(.,~estimate_pareto_N(n = ..6,
                                           lambda = ..27,
                                           xmin = ..4,
                                           xmin2 = 0.006,
                                           xmax = ..5)),
           n_est_l = pmap_dbl(.,~estimate_pareto_N(n = ..6,
                                                   lambda = ..28,
                                                   xmin = ..4,
                                                   xmin2 = 0.006,
                                                   xmax = ..5)),
           n_est_u = pmap_dbl(.,~estimate_pareto_N(n = ..6,
                                                   lambda = ..29,
                                                   xmin = ..4,
                                                   xmin2 = 0.006,
                                                   xmax = ..5)),
           b_old = m_old * n_tot,
           b_est = exp(lmbar_n_est) * n_est,
           lb_est = log(b_est),
           b_est_l = exp(lmbar_n_est_l) * n_est_l,
           b_est_u = exp(lmbar_n_est_u) * n_est_u,
           b_diff = b_est - b_m2,
           b_diff_l = b_est_l - b_m2,
           b_diff_u = b_est_u -b_m2,
           ln_est = log(n_est),
           lmbar_n_est_met = log(exp(lmbar_n_est)^0.75),
           lmbar_b_est_met = log(exp(lmbar_b_est)^0.75)) %>% 
  mutate(across(c(ln_est, lmbar_n_est, lmbar_b_est, lmbar_n_est_met, lmbar_b_est_met), ~as.numeric(scale(.x, center =TRUE, scale = FALSE)), .names = "{.col}_s")) %>% 
  ungroup %>% 
  mutate(n_mean = mean(n_est), .by = 'site_id')

dat_summ = dat %>% 
  summarise(across(c(n_tot, ln_tot, mbar_n, mbar_n_met, mbar_b, mbar_b_met, lmbar_n, lmbar_n_met, lmbar_b, lmbar_b_met, b_m2, lb_m2, m_max, ln_tot_s, lmbar_n_met_s,lmbar_b_met_s, lmbar_n_s, lmbar_b_s, log_gpp_s, log_om_s, mat_s, lambda_med, lower_lambda, upper_lambda, n_est, b_old, b_est, ln_est, lb_est, lmbar_n_est, lmbar_b_est, lmbar_n_est_met, lmbar_b_est_met, lat), mean),
            hill_0 = unique(hill_0), Lhill_0 = unique(Lhill_0), .by ='site_id') %>% 
  mutate(across(c(ln_est, lmbar_n_est, lmbar_b_est, lmbar_n_est_met, lmbar_b_est_met), ~as.numeric(scale(.x, center =TRUE, scale = FALSE)), .names = "{.col}_s"))

# remove the unneeded objects
rm("lambdas", "dw_dat", "dw_dat_temp", "dw_dat_summ", "sampleParams") 
```

# Introduction

Understanding the connections between the environment, biodiversity, and ecological function has been a driving question in ecology [@vanderplas2019].

The extension of BEF frameworks from single trophic level, mainly plant communities, to multi-trophic communities has been met with a number of difficulties. Multi-trophic communities encompass diverse organisms with complex direct and indirect species-species interactions that range from mutualistic to antagonistic, and these are further complicated by the fact that the nature of these interactions are themselves dependent on the environmental conditions, community composition, and the emergence of species interactions networks that vary in both space and time. 

Allometric theory (**AT**) has proved a useful framework to describe the organization of food web interactions across levels of organization. At its core, allometric theory is an energy-based framework that recognizes the strong relationship between organism body size, $M$, and energy use as $I = M^{\alpha}$, where $I$ is individual metabolic rate, $M$ individual body mass, and the metabolic scaling exponent, $\alpha$. The scaling of metabolism with mass is predicted to vary from 0.6 to 1, with a central tendency $\approx$ 0.75 [@west1997; @brown2004; @white2022]. From this relationship, AT represents a null model such that, under assumed conditions of finite and equally distributed resource availability, organism density should decline with $M$ and the extent of decline should reflect the metabolism--mass scaling relationship, $\alpha$ as, $N \propto M^{-\alpha}$. This prediction can be logically extended to multi-trophic communities [@gillooly2003], by including some additional assumption. Within a single trophic level, organism density should    s one of the most widely observed phenomena that is proposed by AT. Specifically, AT predicts that organism density is negatively related to body size across indi

However, $M$ also encapsulates a wealth of other ecological information that is associated with variability in a number of variables from individuals to whole ecosystems species, including: metabolic rate, growth rate, life history, feeding relationships, community biomass and energy throughput [@gillooly2003; @schramski2015].

Increasingly, the distribution of body sizes in populations and food webs has been identified as an integrative measure of ecological status.  The focus on a key organismal trait, body size, derives from body sizes importance 


## Richness models


```{r richness models}
output = 
  capture.output(
    brm(
      bf(lb_est ~ Lhill_0 + (1 |site_id)),
      data = dat,
      family = gaussian(link = 'identity'),
      iter = 2000,
      thin = 1,
      file_refit = 'on_change',
      file = here("data/models/b_s"),
      chains = 4,
      cores = 4,
      seed = 1312,
      save_pars = save_pars(all = TRUE)
      )
    )

b_s_lmm = readRDS(here("data/models/b_s.rds"))
# bayes_R2(b_s_lmm)
# bayes_factor(b_s_full_lmm, b_s_lm)
b_s_cond = conditional_effects(b_s_lmm) %>% flatten %>% data.frame
b_s_lmm_int =fixef(b_s_lmm)[1,'Estimate']
b_s_lmm_hill = fixef(b_s_lmm)[2,]
b_s_lmm_pred = predict(b_s_lmm, newdata = dat %>% dplyr::select(site_id, Lhill_0))
b_s_draws = unlist(as_draws_df(b_s_lmm, variable = 'b_Lhill_0')$b_Lhill_0)

perc_pos_hill = ecdf(b_s_draws)
# 1 - perc_pos_hill(0)
# quantile(b_s_draws, c(0.025, 0.975))

# create a prediction data set
b_s_pred = dat %>%
   modelr::data_grid(site_id = site_id,
            Lhill_0 = Lhill_0) %>%
  add_epred_draws(b_s_lmm, ndraws = 100, re_formula = NA)

# set biomass 
b_breaks = log(c(1e2, 1e3, 1e4, 1e5, 1e6))
b_labels = c(100, 1000, format(c(1e4,1e5,1e6), scientific = TRUE, digits = 2))
# S_breaks = seq.int(floor(min(log(dat$hill_0))), ceiling(max(log(dat$hill_0))), by = 0.25)
S_breaks = log(c(25, 50, 75, 100, 125, 150))
S_labels = format(exp(S_breaks), scientific = FALSE, digits = 2)
s_text_annotation = paste0("$\\theta =$",eval(round(b_s_lmm_hill[1],2)), " [", eval(round(b_s_lmm_hill[3],2)), " , ", eval(round(b_s_lmm_hill[4],2)), "]")
s_text_annotation2 = paste0("$r^{2} =$", eval(round(bayes_R2(b_s_lmm)[1],2)) )

b_s_pred_plot = b_s_pred %>% 
  ggplot()+
  # geom_path(aes(x = Lhill_0, y = .epred, group = .draw), color = 'darkgrey', alpha = 0.5)+
  geom_ribbon(data = b_s_cond, aes(x = Lhill_0, ymin = lower__, ymax = upper__), fill = 'grey', alpha = 0.5)+
  geom_path(data = b_s_cond , aes(x = Lhill_0, y = estimate__), color = 'darkgrey', linewidth = 1)+
  geom_point(data = dat, aes(x = Lhill_0, y = lb_est, fill = site_id), shape = 21, color = 'grey', alpha = 0.5, position = position_jitter(width = 0.02))+
  geom_point(data = dat_summ, aes(x = Lhill_0, y = lb_est, fill = site_id), color = 'black', shape = 21, size = 3)+
  scale_x_continuous(name = expression("Species richness ("*Hill["q=0"]*")"),
                     breaks = S_breaks,
                     labels = S_labels,
                     limits = c(log(25),log(150)),
                     expand = c(0.01,0.01)
                     )+
  scale_y_continuous(name = expression("Biomass (mg "~m^-2*")"),
                     limits = c(log(100),log(10^(6.5))),
                     breaks = b_breaks,
                     labels = b_labels,
                     expand = c(0.01,0.01)
                     )+
  scale_fill_viridis(discrete = TRUE)+
  annotate('text', x = -Inf, y = Inf, vjust = 2, hjust = 0, parse = TRUE, label = TeX(s_text_annotation), family = 'serif' )+
  annotate('text', x = -Inf, y = Inf, vjust = 3, hjust = 0, parse = TRUE, label = TeX(s_text_annotation2), family = 'serif' )+
  theme(legend.position = 'none',
        panel.grid.minor = element_blank());b_s_pred_plot
saveRDS(b_s_pred_plot, here('doc/plots/b_s_pred_plot.rds'))

```

BEF frameworks suggest higher community species richness should lead to higher community biomass. We estimated the biomass~richness scaling relationship, $\theta$, which represents the relationship, $log(B) \propto log(S)$, with richness measured as the Hill number = 0 ($hill_0$). Community biomass had a `r round((1 - perc_pos_hill(0.001))*100,1)` probability of a positively scaling with species richness ($\theta$ = `r round(b_s_lmm_hill[1], 2)` [`r round(quantile(b_s_draws, c(0.025)),2)` -- `r round(quantile(b_s_draws, c(0.975)),2)`]; mean $\pm$ 95% credible interval [CrI]), with ~`r round(bayes_R2(b_s_lmm)[1]*100)`% of the variation in across stream community biomass explained by richness. 

## Allometric models

```{r allometric models}
output = 
  capture.output(
    brm(
      bf(lb_est ~ lmbar_b_est + (1 + lmbar_b_est | site_id)),
      data = dat,
      family = gaussian(link = 'identity'),
      iter = 5000,
      thin = 1,
      file_refit = 'on_change',
      file = here("data/models/b_m"),
      control = list(adapt_delta = 0.999),
      chains = 4,
      cores = 4,
      seed = 1312
      )
    )

b_m_lmm = readRDS(here("data/models/b_m.rds"))
b_m_draws = unlist(as_draws_df(b_m_lmm, variable = 'b_lmbar_b_est')$b_lmbar_b_est)
# bayes_R2(b_m_lmm)[1]
perc_pos_m = ecdf(b_m_draws)
# 1 - perc_pos_m(0.001)

b_m_lmm_int =fixef(b_m_lmm)[1,'Estimate']
b_m_lmm_fix = fixef(b_m_lmm)[2,]
b_m_cond = conditional_effects(b_m_lmm) %>% flatten %>% data.frame
# b_m_lm_pred = predict(b_m_lm, newdata = dat %>% dplyr::select(site_id, lmbar_b_met))

## remove the two streams with no fish
# output = 
#   capture.output(
#     brm(
#       bf(lb_est ~ lmbar_b_met + (1 + lmbar_b_met| site_id)),
#       data = dat %>% filter(site_id %ni% outlier_sites),
#       family = gaussian(link = 'identity'),
#       iter = 5000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_m_no-outliers"),
#       control = list(adapt_delta = 0.999),
#       chains = 4,
#       cores = 4,
#       seed = 1312
#       )
#     )
# 
# b_m_lmm_outliers = readRDS(here("data/models/b_m_no-outliers.rds"))
# bayes_R2(b_m_lmm_outliers)

# b_m_lmm_outliers_int =fixef(b_m_lmm_outliers)[1,'Estimate']
# b_m_lmm_outliers_fix = fixef(b_m_lmm_outliers)[2, 'Estimate']
# b_m_outliers_cond = conditional_effects(b_m_lmm_outliers) %>% flatten %>% data.frame

b_m_pred = dat %>% 
  modelr::data_grid(site_id = site_id,
            lmbar_b_est = lmbar_b_est) %>% 
  add_epred_draws(b_m_lmm, ndraws = 100, re_formula = NA)

# b_m_outliers_pred = dat %>% 
#   modelr::data_grid(site_id = site_id,
#             lmbar_b_met = lmbar_b_met) %>% 
#   add_epred_draws(b_m_lmm_outliers, ndraws = 100, re_formula = NA)

# set biomass 
b_breaks = log(c(1e2, 1e3, 1e4, 1e5, 1e6))
b_labels = c(100, 1000, format(c(1e4,1e5,1e6), scientific = TRUE, digits = 2))
# M_breaks = seq.int(round(min(dat$lmbar_b_met, na.rm = TRUE)), round(max(dat$lmbar_b_met, na.rm = TRUE)), by = 2)
# convert log e to log 10 for estimation of 
M_breaks = log(c(10,100,1000, 1e4))
M_labels = exp(M_breaks)#format(exp(M_breaks), scientific = FALSE, digits = NULL, nsmall = 0)
r2_lab = round(bayes_R2(b_m_lmm)[1],2)

m_text_annotation = paste0('$\\beta =$', eval(round(b_m_lmm_fix[1],2)), " [", eval(round(b_m_lmm_fix[3],2)), " , ", eval(round(b_m_lmm_fix[4],2)), "]")
m_text_annotation2 = paste0('$r^2=$',eval(round(bayes_R2(b_m_lmm)[1],2)))

b_m_pred_plot = b_m_pred %>% 
  ggplot()+
  geom_ribbon(data = b_m_cond, aes(x = lmbar_b_est, ymin = lower__, ymax= upper__), fill = 'grey', alpha = 0.5)+
  geom_path(data = b_m_cond, aes(x = lmbar_b_est, y = estimate__), color = 'darkgrey', linewidth = 1)+
  #add outliers regression in 
    # geom_ribbon(data = b_m_outliers_cond, aes(x = lmbar_b_met, ymin = lower__, ymax= upper__), fill = 'darkgreen', alpha = 0.5)+
  # geom_path(data = b_m_outliers_cond, aes(x = lmbar_b_met, y = estimate__), color = 'darkgreen', linewidth = 1)+
  # geom_path(aes(x = lmbar_b_met, y = .epred, group = .draw), color = 'darkgrey', alpha = 0.5)+
  geom_point(data = dat, aes(x = lmbar_b_est, y = lb_est, fill = site_id), shape = 21, color = 'grey', alpha = 0.5, position = position_jitter(width = 0.02))+
  geom_point(data = dat_summ, aes(x = lmbar_b_est, y = lb_est, fill = site_id), color = 'black', shape = 21, size = 3)+
  scale_x_continuous(name = expression(bar(M)[" bio-weighed"]*"(mg "*ind.^-1*")"),
                     breaks = M_breaks,
                     labels = M_labels,
                     limits = c(NA,NA))+
  scale_y_continuous(name = expression("Biomass (mg "~m^-2*")"),
                     limits = c(log(100),log(10^(6.5))),
                     breaks = b_breaks,
                     labels = b_labels,
                     expand = c(0.01,0.01)
                     )+
  scale_fill_viridis(discrete = TRUE)+
  annotate('text', x = -Inf, y = Inf, vjust = 2, hjust = 0, parse = TRUE, label = TeX(m_text_annotation), family = 'serif')+
  annotate('text', x = -Inf, y = Inf, vjust = 3, hjust = 0, parse = TRUE, label = TeX(m_text_annotation2), family = 'serif')+
  theme(legend.position = 'none',
        panel.grid.minor = element_blank());b_m_pred_plot
saveRDS(b_m_pred_plot, here('doc/plots/b_m_pred_plot.rds'))

```

Alternatively, allometric theory predicts community biomass should scale with mean community body size ($\overline M$). We estimated the biomass~$\overline M$ scaling relationship, $\beta$, which represents the relationship, $log(B) \propto log(\overline M)$, with $\overline M$ calculated as the mean community body size weighted by relative biomass in the community, $\overline M_{B-weighted}$. Community biomass had a strong, consistent positive scaling with $\overline M$, and this relationship was steeper than the 0.25 predicted by AT ($\beta$ = `r round(b_m_lmm_fix[1], 2)` [`r round(quantile(b_m_draws, c(0.025)),2)` -- `r round(quantile(b_m_draws, c(0.975)),2)`]; mean $\pm$ 95% CrI), with ~`r round(bayes_R2(b_m_lmm)[1]*100)`% of the variation in across stream community biomass explained by $\overline M$.

## Allometric predictions

```{r allometric prediction}

output = 
  capture.output(
    brm(bf(ln_est_s~lmbar_b_est_s + (1 + lmbar_b_est_s|site_id)),
        data = dat,
        family = gaussian(link = 'identity'),
        iter = 2000,
        thin = 1,
        file_refit = 'on_change',
        file = here("data/models/NM_bwt"),
        control = list(adapt_delta = 0.99),
        chains = 4, cores = 4,
        seed = 1312
        )
    )
NM_bwt = readRDS(here("data/models/NM_bwt.rds"))
# NM_met_nwt = readRDS(here('data/models/NM_nwt.rds'))
# plot(conditional_effects(NM_met_bwt))

NM_bwt_cond = conditional_effects(NM_bwt) %>% flatten %>% data.frame 

NM_bwt_int =fixef(NM_bwt)[1,'Estimate']
NM_bwt_slope = fixef(NM_bwt)[2,]

# data grid for mean prediction
NM_bwt_pred = dat %>% 
  modelr::data_grid(lmbar_b_est_s = lmbar_b_est_s) %>% 
  mutate(pred_s = NM_bwt_int + lmbar_b_est_s *-1) %>% 
  # if we want estimates around predictions we can call this later
  add_epred_draws(NM_bwt, ndraws = 100, re_formula = NA) %>%
  left_join(dat %>% dplyr::select(site_id, lmbar_b_est_s, ln_est_s, lambda_med, Lhill_0), by = 'lmbar_b_est_s') %>%
  # mutate(lmbar_n_est_met = lmbar_n_est_met * sd(dat$lmbar_n_est_met, na.rm = TRUE) + mean(dat$lmbar_n_est_met, na.rm = TRUE),
         # pred = pred_s * sd(dat$ln_est, na.rm = TRUE) + mean(dat$ln_est,na.rm = TRUE),
         # ln_est = ln_est * sd(dat$ln_est, na.rm = TRUE) + mean(dat$ln_est, na.rm = TRUE)) %>%
  mutate(resid_theory = ln_est_s - pred_s)#,
         # resid_theory = ln_est - pred)

## values for rescaling
ln_est_center = mean(dat_summ$ln_est)
lmbar_b_est_center = mean(dat_summ$lmbar_b_est)


M_breaks = log(c(0.001,0.01,0.1, 1,10,100,1000,1e4))-lmbar_b_est_center
M_labels = c(0.001,0.01,0.1, 1,10,100,1000,1e4)

N_breaks = log(c(1e3, 1e4, 1e5, 1e6, 1e7)) - ln_est_center
N_labels = c(format(c(1e3, 1e4), scientific = FALSE, digits= 2), format(c(1e5, 1e6, 1e7), scientific = TRUE, digits = 2))

NM_text_annotation = paste("italic('N ~')","~italic('M')^~-1")
# x_axis_label =paste0("$\\bar{M}$")#^{0.75}}$")#_{B weighted}$","$sub{B weighed}$","$\\quad$", "(mg ","$ind^{-1})$")

nm_theory_plot=
dat %>% 
  ggplot()+
  geom_line(data = NM_bwt_pred, aes(x = lmbar_b_est_s, y = pred_s), color = 'black', linewidth = 1)+
  geom_point(aes(x = lmbar_b_est_s, y = ln_est_s, fill = site_id),shape = 21, color = 'darkgrey', alpha = 0.5)+
  geom_point(data = dat_summ, aes(x = lmbar_b_est_s, y = ln_est_s, fill = site_id), color = 'black', shape = 21, size = 3)+
  geom_line(data = NM_bwt_cond, aes(x = lmbar_b_est_s, y = estimate__), color = 'darkgrey')+
  geom_ribbon(data = NM_bwt_cond, aes(x = lmbar_b_est_s, ymin = lower__, ymax = upper__), alpha = 0.5, fill = 'grey')+
  scale_x_continuous(name = expression(~bar(M)["bio-weighted"]~"(mg "*individual^-1*")"),
                     breaks = M_breaks,
                     labels = M_labels,
                     limits = c(NA,NA),
                     expand = c(0.01,0.01))+
  scale_y_continuous(name = expression("Abundance (individuals   "~m^-2~")"),
                     breaks = N_breaks,
                     labels = N_labels,
                     expand = c(0.01,0.01))+
  coord_cartesian(ylim = c(NA, (log(10^(6.5))-ln_est_center)))+
  scale_fill_viridis(discrete = TRUE)+
  annotate('text', x= -Inf, y = Inf, vjust = 1, hjust = -0.5, parse = TRUE, label = NM_text_annotation, family = 'serif' )+
  theme(legend.position = 'none');nm_theory_plot
saveRDS(nm_theory_plot, here('doc/plots/n_m_theory_plot.rds'))


```

As suggested by the steeper $B \propto \overline M$ scaling, the scaling of community abundance ($N$) with $\overline M$ was shallower than the the -1 predicted by theory. This predicted relationship $N \sim \overline M^{-1}$ represents the line of constant yield, or the line of constant biomass for communities of different $\overline M$. The estimated $N \propto \overline M$ relationship was consistently negative, with a mean estimated scaling slope of `r round(NM_bwt_slope[1],2)` [`r round(NM_bwt_slope[3],2)` -- `r round(NM_bwt_slope[4],2)` 95% CrI]. This relationship agrees with the patterns in $B \propto \overline M$ that stream communities with larger $\overline M$ have more individuals and support more biomass than communities with smaller $\overline M$, even after we account for $\overline M$. This gives us a framework to explore the differences in how communities "overyield" or maintain higher biomass than expected at a given body size. To do this, we can calculate the deviations from AT predictions, which reflect the under- and over-yielding of communities away from a constant biomass yield. 

## Residual models

```{r residual models}
## calculate the bayesian linear regression
NM_bwt_resid = dat %>% 
  mutate(pred_s = predict(NM_bwt)[,1]) %>% 
  mutate(pred_theory = NM_bwt_int + lmbar_b_est_s *-1,
         resid_theory = pred_s - pred_theory)
output =
  capture.output(
    brm(
      bf(resid_theory ~ Lhill_0 + lambda_med + (1 + lambda_med | site_id)),
      data = NM_bwt_resid,
      family = gaussian(link = 'identity'),
      iter = 5000,
      thin = 1,
      file_refit = 'always',
      file = here("data/models/resid_s_lambda"),
      control = list(adapt_delta = 0.99),
      chains = 4, cores = 4,
      seed = 1312,
      save_pars = save_pars(all = TRUE)
      )
    )
# load the full model
resid_s_lambda = readRDS(here('data/models/resid_s_lambda.rds'))

b_resid_marg_lambda = ggeffects::predict_response(resid_s_lambda, terms = c('lambda_med'), margin = 'marginalmeans', type = 'fixed') %>% 
  rename(lambda_med = 'x', resid_theory = 'predicted')
# plot(b_resid_marg_lambda)
b_resid_marg_hill = ggeffects::predict_response(resid_s_lambda, terms = c('Lhill_0'), margin = 'marginalmeans', type = 'fixed') %>% 
  rename(Lhill_0 = 'x', resid_theory = 'predicted')
# plot(b_resid_marg_hill)


### metabolic mass models
NM_bwt_resid  %>%
  ggplot()+
  geom_line(data = b_resid_marg_hill, aes(x = Lhill_0, y = resid_theory), color = 'darkgrey')+
  geom_ribbon(data = b_resid_marg_hill, aes(x = Lhill_0, ymin = conf.low, ymax = conf.high),fill = 'grey', alpha = 0.5)+
  geom_point(aes(x = Lhill_0, y = resid_theory, fill = site_id), color = 'darkgrey', shape =21, alpha = 0.5)+
  geom_point(data = . %>% ungroup %>%  summarise(Lhill_0 = mean(Lhill_0, na.rm = TRUE),
                                    resid_theory = mean(resid_theory, na.rm = TRUE),.by = 'site_id'),
             aes(x = Lhill_0, resid_theory, fill = site_id), color = 'black', shape = 21, size = 3)+
  scale_fill_viridis(discrete = TRUE)+
  theme(legend.position = 'none')
# 
NM_bwt_resid %>%
  ggplot()+
  geom_line(data = b_resid_marg_lambda, aes(x = lambda_med, y = resid_theory), color = 'darkgrey')+
  geom_ribbon(data = b_resid_marg_lambda, aes(x = lambda_med, ymin = conf.low, ymax = conf.high),fill = 'grey', alpha = 0.5)+
  geom_point(aes(x = lambda_med, y = resid_theory, fill = site_id), color = 'black', shape = 21, alpha = 0.5)+
  geom_point(data = NM_bwt_pred %>% ungroup %>% summarise(labmda_med = mean(lambda_med, na.rm = TRUE),
                                    resid_theory = mean(resid_theory, na.rm = TRUE),
                                    lambda_med = mean(lambda_med),.by = 'site_id'),
             aes(x = lambda_med, resid_theory, fill = site_id), color = 'black', shape = 21, size = 3)+
  scale_fill_viridis(discrete = TRUE)+
  theme(legend.position = 'none')
# 
# 
# output = capture.output(
#   brm(
#     bf(ln_est~lmbar_n_est_met),#+(1 + lmbar_b_met_s|site_id)),
#     data = dat,
#     family = gaussian(link = 'identity'),
#     iter = 1000,
#     thin = 1,
#     file_refit = 'on_change',
#     file = here("data/models/NM_met_bwt"),
#     control = list(adapt_delta = 0.9),
#     chains = 4, cores = 4,
#     seed = 1312
#     )
#   )
# NM_met_bwt = readRDS(here("data/models/NM_met_bwt.rds"))
# NM_met_bwt_int =fixef(NM_met_bwt)[1,'Estimate']
# 
# NM_met_bwt_pred = dat %>% 
#   data_grid(lmbar_b_met_s = lmbar_b_met_s) %>%
#   mutate(pred = NM_met_bwt_int + lmbar_b_met_s*-1) %>% 
#   left_join(dat %>% dplyr::select( site_id, lmbar_b_met_s, ln_tot_s, lambda_med, log_gpp_s,log_om_s), by = 'lmbar_b_met_s') %>% 
#   mutate(resid_theory = ln_tot_s - pred)
# 
# ## raw body mass models
# output = capture.output(
#   brm(
#     bf(ln_tot_s~lmbar_n_s),
#     data = dat,
#     family = gaussian(link = 'identity'),
#     iter = 1000,
#     thin = 1,
#     file_refit = 'on_change',
#     file = here("data/models/NM_nwt"),
#     chains = 4, cores = 4,
#     sample_prior = 'yes',
#     save_pars = save_pars(all = TRUE),
#     seed = 1312
#     )
#   )
# 
# NM_nwt = readRDS(here("data/models/NM_nwt.rds"))
# NM_nwt_int =fixef(NM_nwt)[1,'Estimate']
# 
# # NM_nwt_ranef = ranef(NM_nwt)$site_id
# # NM_nwt_slopes = NM_nwt_ranef[,,'lmbar_n0.75_s']
# 
# NM_nwt_pred = dat %>% 
#   data_grid(lmbar_n_s = lmbar_n_s) %>% 
#   mutate(pred = NM_nwt_int + lmbar_n_s*-1)%>% 
#   left_join(dat %>% dplyr::select(site_id, lmbar_n_s, ln_tot_s, lambda_med, log_gpp_s, log_om_s), by = 'lmbar_n_s') %>% 
#   mutate(resid_theory = ln_tot_s - pred)
# 
# output = 
#   capture.output(
#     brm(
#       bf(ln_tot_s~lmbar_b_s),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 1000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/NM_bwt"),
#       chains = 4, cores = 4,
#       seed = 1312
#       )
#     )
# NM_bwt = readRDS(here("data/models/NM_bwt.rds"))
# NM_bwt_int =fixef(NM_bwt)[1,'Estimate']
# 
# NM_bwt_pred = dat %>% 
#   data_grid(lmbar_b_s = lmbar_b_s) %>%
#   mutate(pred = NM_bwt_int + lmbar_b_s*-1) %>% 
#   left_join(dat %>% dplyr::select( site_id, lmbar_b_s, ln_tot_s, lambda_med, log_gpp_s,log_om_s), by = 'lmbar_b_s') %>% 
#   mutate(resid_theory = ln_tot_s - pred)

```

## Richness predictions

```{r richness prediction}
# output = 
#   capture.output(
#     brm(
#       bf(lb_est ~ Lhill_0 + lambda_med + (1 + lambda_med |site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 2000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_s_full"),
#       control = list(adapt_delta = 0.99),
#       chains = 4,
#       cores = 4,
#       seed = 1312
#       )
#     )
# 
# b_s_full_lmm = readRDS(here("data/models/b_s_full.rds"))
# bayes_R2(b_s_full_lmm)[1]
# 
# # plot_predictions(b_s_full_lmm, condition = c('hill_0', 'lambda_med'), points = 1)
# 
# # b_m_marg = ggeffects::predict_response(b_s_full_lmm, terms = c('lambda_med'), margin = 'marginalmeans', type = 'fixed')
# b_m_marg = ggeffects::predict_response(b_s_full_lmm, terms = dat %>% dplyr::select(Lhill_0), margin = 'marginalmeans', type = 'fixed')
# plot(b_m_marg)
# 
# 
# b_s_lmm_int =fixef(b_s_full_lmm)[1,'Estimate']
# b_s_lmm_hill = fixef(b_s_full_lmm)[2,'Estimate']
# b_s_lmm_lambda = fixef(b_s_full_lmm)[3, 'Estimate']
# b_s_lm_pred = predict(b_s_lm, newdata = dat %>% dplyr::select(site_id, hill_0))

# b_s_full_pred = dat %>%
#   data_grid(site_id = site_id,
#             hill_0 = hill_0,
#             lambda_med = lambda_med) %>% 
#   add_epred_draws(b_s_full_lmm, ndraws = 100, re_formula = NA)#~(1 + lambda_med |site_id))

# b_breaks = seq.int(round(min(dat$lb_est, na.rm = TRUE)), round(max(dat$lb_est, na.rm = TRUE)), by = 2)
# b_labels = format(exp(b_breaks), scientific = TRUE, digits = 2)
# # S_breaks = seq.int(floor(min(log(dat$hill_0))), ceiling(max(log(dat$hill_0))), by = 0.25)
# 
# lambda_breaks = c(-1.5, -2.0, -2.5, -3.0)
# lambda_labels = format(lambda_breaks, scientific = FALSE, digits = 2)
# lambda_text_annotation = paste0("(ln(B) | S)","$\\approx$",eval(round(b_s_lmm_lambda,2)),"$\\times$","\\lambda")
# 
# b_lambda_pred_plot = b_m_marg %>% 
#   rename(lambda_med = x, lb_est = predicted) %>% 
#   ggplot()+
#   geom_ribbon(aes(x = lambda_med, ymin = conf.low, ymax = conf.high), fill = 'grey', alpha = 0.5)+
#   geom_path(aes(x = lambda_med, y = lb_est), color = 'darkgrey', linewidth = 1)+
#   geom_point(data = dat, aes(x = lambda_med, y = lb_est, fill = site_id), shape = 21, color = 'grey', alpha = 0.5)+
#   geom_point(data = dat %>% summarise(
#     lambda_med = mean(lambda_med, na.rm = TRUE),
#   lb_est = mean(lb_est, na.rm = TRUE),.by = 'site_id'),
#   aes(x = lambda_med, y = lb_est, fill = site_id), color = 'black', shape = 21, size = 3)+
#   scale_x_continuous(name = TeX(paste0("\\lambda")),#, expression("Species richness ("*Hill["q=0"]*")"),
#                      breaks = lambda_breaks,
#                      labels = lambda_labels,
#                      limits = c(-3.1,-1.25))+
#   scale_y_continuous(name = expression("Biomass (mg "~m^-2~")"),
#                      limits = c(7.675,16.22),
#                      breaks = b_breaks,
#                      labels = b_labels
#   )+
#   scale_fill_viridis(discrete = TRUE)+
#   annotate('text', x = -Inf, y = Inf, vjust = 2, hjust = 0, parse = TRUE, label = TeX(lambda_text_annotation, output = 'character'), family = 'serif' )+
#   annotate('text', x = -Inf, y = Inf, vjust = 3, hjust= 0, parse = TRUE, label = TeX(paste0("Full model: $r^2$","=",round(bayes_R2(b_s_full_lmm)[1],2)), , output = 'character'), family = 'serif')+
#   theme(legend.position = 'none');b_lambda_pred_plot
# saveRDS(b_lambda_pred_plot, here('doc/plots/b_lambda_pred_plot.rds'))

# b_s_resid%>% 
#   ungroup %>% 
#   summarise(.residual_med = median(.residual),
#             lambda_med = median(lambda_med), .by = c(site_id, sample_id)) %>% 
#   ggplot()+
#   geom_point(aes(x = lambda_med, y = .residual_med, fill = site_id), color = 'darkgrey', shape = 21, alpha = 0.5 )+
#   geom_point(data = . %>% summarise(.residual_med = mean(.residual_med),
#                                     lambda_med = mean(lambda_med), .by = site_id),
#              aes(x = lambda_med, y = .residual_med, fill = site_id), color = 'black', shape = 21, size = 3)+
#   scale_fill_viridis(discrete = TRUE)+
#   theme(legend.position = 'none')
```



## Richness extrapolation

```{r richness extrapolated}
# output = 
#   capture.output(
#     brm(bf(ln_est ~Lhill_0 + (1 |site_id)),
#         data = dat,
#         family = gaussian(link = 'identity'),
#         iter = 5000,
#         thin = 1,
#         file_refit = 'on_change',
#         file = here("data/models/n_s_est"),
#         control = list(adapt_delta = 0.99),
#         chains = 4, cores = 4,
#         seed = 1312
#         )
#     )
# 
# n_s_est = readRDS(here("data/models/n_s_est.rds"))
# 
# 
# output = 
#   capture.output(
#     brm(bf(lb_est~Lhill_0 + (1 |site_id)),
#         data = dat,
#         family = gaussian(link = 'identity'),
#         iter = 2000,
#         thin = 1,
#         file_refit = 'on_change',
#         file = here("data/models/b_s_est"),
#         control = list(adapt_delta = 0.99),
#         chains = 4, cores = 4,
#         seed = 1312
#         )
#   )
# 
# 
# output = 
#   capture.output(
#     brm(
#       bf(lb_est ~ Lhill_0 + (1 |site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 1000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/best_s"),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#       )
#     )
# 
# output = 
#   capture.output(
#     brm(
#       bf(lb_est ~ lambda_med + (1 |site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 1000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/best_lambda"),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#       )
#     )
# 
# best_lambda_lmm = readRDS(here("data/models/best_lambda.rds"))
# best_s_lmm = readRDS(here("data/models/best_s.rds"))
# 

```



## Full model 

```{r full richness lambda model}

# output = 
#   capture.output(
#     brm(
#       bf(lb_est ~ Lhill_0 + lambda_med + (1 + lambda_med |site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 2000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_s_full"),
#       control = list(adapt_delta = 0.99),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#       )
#     )
# 
# b_s_full_lmm = readRDS(here("data/models/b_s_full.rds"))

```

## Environmental models

```{r environmental models}

# output =
#   capture.output(
#     brm(
#       bf(lb_est ~ log_gpp_s + I(log_gpp_s^2) + (1 | site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 5000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_gpp"),
#       control = list(adapt_delta = 0.99),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#     )
#   )
# 
# b_gpp_full_lmm = readRDS(here("data/models/b_gpp.rds"))
# 
# b_gpp_cond = conditional_effects(b_gpp_full_lmm) %>% 
#   flatten %>% data.frame
# 
# b_gpp_lm_fix = fixef(b_gpp_full_lmm)[2, 'Estimate']
# perc_pos_gpp = ecdf(unlist(as_draws_df(b_gpp_full_lmm, variable = 'b_log_gpp_s')$b_log_gpp_s))
# 1 - perc_pos_gpp(0)
# quantile(unlist(as_draws_df(b_gpp_full_lmm, variable = 'b_log_gpp_s')$b_log_gpp_s), c(0.025, 0.975))
# 
# 
# output =
#   capture.output(
#     brm(
#       bf(lb_est ~ mat_s + (1 | site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 5000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_mat"),
#       control = list(adapt_delta = 0.99),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#     )
#   )
# 
# b_mat_full_lmm = readRDS(here("data/models/b_mat.rds"))
# 
# output =
#   capture.output(
#     brm(
#       bf(lb_est ~ log_om_s + (1 | site_id)),
#       data = dat,
#       family = gaussian(link = 'identity'),
#       iter = 5000,
#       thin = 1,
#       file_refit = 'on_change',
#       file = here("data/models/b_om"),
#       control = list(adapt_delta = 0.99),
#       chains = 4,
#       cores = 4,
#       seed = 1312,
#       save_pars = save_pars(all = TRUE)
#     )
#   )
# 
# b_om_full_lmm = readRDS(here("data/models/b_om.rds"))



```





## Theory of body size--abundance

# Methods

We analyzed the community abundance, biomass, and size distributions using 670,816 individual body masses of fish and macroinvertebrates collected by the National Ecological Observatory Network (NEON) from 2016 to 2022. NEON is a continental-scale ecological sampling program that uses standardized, automated sensor measurements coupled with observational field data and biological collections repeated across seasons (spring, summer, autumn), years (2015 to present), and space (across North America) (Fig. 2). The final data set included 59,083 measures from 114 fish species and 611,733 measures from 1,125 macroinvertebrates taxonomic groups (typically genus or species). The samples were typically collected 2-3 times per year at each of 21 sites, resulting in a total of 115 unique collection events. Below we describe how the data sets were merged to contain both fish and macroinvertebrates. Further details including a schematic overview of this workflow along with a step-by-step example of the fish resampling procedure, is provided in the supplemental materials of [@gjoni2026].

### Macroinvertebrates

NEON collected macroinvertebrate data via fixed-area samplers (e.g., Surber/Core/Kicknet) and measured insect body lengths to the nearest mm along with estimates of their density (individuals $m^{-2}$). While the samplers vary based on the stream characteristics (e.g., core samplers, Surber samplers, etc), all mesh sizes are the same (243 $\mu m$). Measurements of macroinvertebrate lengths spanned from 1 to 86 mm. We converted them to dry mass (mg) with published taxon-specific length-mass regressions [see @pomeranz2022]. 

### Fish

Fish were collected from each site twice per year (typically) using 3-pass removal electrofishing. For each collection, the first 50 fish per taxon were measured for wet mass (wm) in g (NEON 2022). We converted this to dry mass (dm) using the equation $dm = 0.2\times wm$ [@brey2010]. The remaining fish were tallied as a bulk count per species (without individual mass measures). Because individual body masses were measured only for a subset of individuals, raw measurements alone would not reflect “true” species abundances, particularly when total abundance varied widely among taxa. Using the three-pass depletion data, we estimated fish population density (individuals $m^{-2}$) in each collection using a multinomial Poisson depletion model [@royle2004]. We specified the model in R using the `ubms` package [@kellner2022]. The response variable was the number of fish caught per pass and the predictor variable was the collection id (site+date+reach = collection id). The model resulted in a population estimate for each collection, which we converted to individuals $m^{-2}$ by dividing each estimate by the sampled area (mean stream width x length of the electrofishing sample). We then multiplied that population estimate by the relative abundance of each fish species, resulting in an estimated density (individuals $m^{-2}$) of each fish species in each collection. Finally, we merged those estimates with the dry mass measurements and resampled the dry mass measures with replacement, weighted by species-specific density. This ensured that more abundant species contributed proportionally more individuals to the reconstructed size distribution, even when the number of measured body sizes was similar across taxa. An example of this procedure is given in Fig. S2 of [@gjoni2026]. Weighting by individuals per no/10,000 $m^{-2}$ instead of individuals $M^{-1}$ was necessary to ensure that enough body sizes were sampled (i.e., individuals $m^{-2}$ was typically <1). For each collection, we then summed the total number of individual body sizes and averaged their density estimates, resulting in a dataset containing individual-level body sizes (rather than species mean) estimates and their associated density for each collection [@gjoni2026].

### Combining fish and macroinvertebrates

Fish and macroinvertebrates were collected on different dates, with macroinvertebrates collected three times per year and fish collected twice. Therefore, to combine fish and macroinvertebrate samples, we limited the data to only collections that occurred within 30 days of each other. For example, if macroinvertebrates were collected on June 10 and fish collected on June 20, those samples were combined. If more than one sample was in the 30-day window (e.g., another fish collection on June 21), we selected the samples collected closest in time to each other in time to the paired collection, retaining only the most recent collection. The resulting data set contains body sizes ranging nine orders of magnitude (0.003 to 200,000 mg dry mass) along with their densities. We used this data set to estimate total community abundance (individuals $m^{-2}$), biomass (mg $m^{-2}$), and the individual size distributions (see Data Analysis). 

## Environmental Data

### Temperature

To estimate mean annual stream temperature for each of the 21 sites, we obtained water temperature readings collected every four hours from 2016 to 2021 using the NEON data (Table S12). We removed data that did not pass NEON quality control checks as noted by NEON. Specifically, we  removed data that appeared unreasonably such as low (< -5°C) or high (> 50°C) temperatures. Some data for Alaskan streams is missing when the water is frozen. For those data, we assumed a temperature of 0°C. The resulting dataset contained 93,930 temperature readings. Temperature was modeled using a Bayesian generalized additive mixed model (GAMM), with a smooth term for temperature and year included as a random effect. Although the model has a generalized additive structure, it was fit within a Bayesian framework, allowing direct estimation of posterior distributions for the temperature effect. To reduce the data size for modeling, we estimated the mean weekly temperature and modeled that as a function of date and site using a Bayesian generalized additive mixed model with a Gaussian likelihood and year as a varying intercept. Mean weekly temperature was centered prior to modeling. This approach allowed us to have a posterior distribution of temperature predictions on each day over three years. From that posterior distribution, we calculated the mean annual temperature and standard deviation (Table 1) for each site.

### Gross Primary Production

We estimated regimes of annual gross primary production (GPP, g C m-2 y-1) through a multistep ensemble model process (https://github.com/jswesner/neon_size_spectra-slim). Daily time series of NEON sensor-based data for temperature, stream discharge, and oxygen concentration (see Table S12) were checked for data quality flags and visually inspected to identify potential errant data. We then estimated daily GPP from cleaned time series with maximum likelihood estimation through 15 different methods using the `streamMetabolizer` package (Appling et al. 2018). Methods varied in respect to discharge–gas exchange, photosynthetic rate–light, and photosynthetic rate–temperature relationships. From this model suite, we first calculated root mean squared error (RMSE) based on pointwise differences between predicted and observed daily oxygen series. This model suite was reduced by removing models that yielded unreasonably high estimates based on mean daily GPP (>13,000 g C m-2 y-1), correlation coefficients >0.95 between reaeration and ecosystem respiration, and particularly poor fits based on RMSE. From this filtered model suite, we created an ensemble model weighted by relative RMSE. Finally, to develop a general model of the GPP regime at each site, we fit a hierarchical generalized additive mixed model (GAMM) to ensemble estimated GPP by ‘day of year’ with ‘year’ treated as a random effect term. We summed the estimated ‘day of year’ fixed effect to quantify annual GPP for all sites. Annual GAMMs were fit with the `brms` package [@bürkner2017] with smoothing functions from the `mgcv` package [@wood2017].

### Organic Matter

We estimated the standing stock of organic matter from 45 unsorted bulk benthic samples in the NEON biorepository (at least two samples per site) [@yule2020]. The samples were collected at the same time as macroinvertebrate samples, using the same collection techniques (i.e., Surber sampler, core sampler). We obtained the raw samples from NEON and first removed macroinvertebrates. We dried the remaining organic matter at 60°C for >48 hours to bring to a constant mass. We then combusted samples at 500°C for four hours before reweighing to determine total organic matter mass. Samples were scaled to areal mass ($g \ m^{-2}$) by dividing total organic mass by the benthic area sampled (e.g., the area of the Surber sampler, core sampler, etc.).

## Data Analysis

To examine how the ISD varied as a function of temperature and resources, we used a Bayesian generalized linear mixed model with a truncated Pareto likelihood. A description and justification of this modelling approach for ISD’s is given in [@wesner2024]. The model structure was:
$$x_ijkl \sim f(x_{jkl}; λ_{jkl},x_{min}_{jkl},x_{max}_{jkl}, counts_{ijkl})$$
$$λ_{jkl}  = a + βZ + γ_{k:j}+ γ_{l} + b_{l}Z$$

where $x_{ijkl}$ is the $i$th body size from sample $j$ in site $k$ and year $l$. The likelihood $f(…)$ is a truncated Pareto with a single free parameter λ_$jkl$, the exponent of the ISD. $x_{min}_{jkl}$ and $x_{max}_{jkl}$ are the minimum and maximum body sizes in each sample, site, and year. 
$x_{min}_{jkl}$ was chosen as the smallest body size in each sample for which the data most closely match a power law using the `estimate_xmin()` function from the `poweRlaw` package [@gillespie2024]. This method ensures that estimates of $\lambda$ are not biased from undersampling of small individuals [@virkar2014]. Each body size has a corresponding density in units of number individuals $m^{-2}$, represented by $counts_{ijkl}$, as described in [@edwards2017a]. $\lambda_{jkl}$ is modeled as a linear function of an intercept $\alpha$ and $\beta Z$ represents the single, two, and three-way interactions of the $Z$ predictors of mean annual temperature, mean annual GPP, and standing stock organic matter. All predictors were standardized as z-scores prior to fitting. Varying intercepts are included for individual sample $j$ nested within sites ($k_{\gamma_{k:j}$) and year ($\gamma_{l}$) along with varying slopes, including interactions, by year $b_{l} Z$. To improve sampling efficiency, the varying intercepts were modeled using non-centered parameterization, which is excluded here for clarity, but is present in the Stan model code: https://github.com/jswesner/neon_size_spectra-slim.

Priors for the intercept were $Normal(-2, 0.5)$, chosen based on theoretical predictions [@reuman2008] and previous analysis of ISD values in streams [@pomeranz2022]. Priors for each $\beta$ parameter were set to $Normal(0, 0.2)$. Priors for the $q$ varying intercepts were $Normal(0, sq)$, with each $sq$ hyperprior set to $Exponential(7)$. These priors were chosen based on prior predictive simulation [@wesner2021] to center the prior probabilities of $\lambda$ between about -2.5 to -1 while still allowing probabilities at very large (e.g., 1) or small values (e.g., -4) (Fig. S31).

### Cross community scaling ($N \sim M$)

To estimate the cross community scaling relationship, we first went through a process to account for systematic undersampling of small individuals in the data set. This is a known problem,




We fit all models in `rstan` [@stan2024] via the `brms` [@bürkner2017] and `isdbayes` [@wesner2023a] packages in R. Model fit was checked using posterior predictive checks and prior influence was checked using prior predictive simulation (Fig. S3-5).



# Results

Total community abundances ranged ~`r (dat %>% dplyr::select(ln_est) %>% max - dat %>% dplyr::select(ln_est) %>% min) %>% round` order of magnitude from `r dat %>% dplyr::select(n_tot) %>% min %>% signif(2) %>% format(scientific = TRUE)` to `r dat %>% dplyr::select(n_tot) %>% max %>% signif(2) %>% format(scientific = TRUE)` with average community abundance of `r dat %>% dplyr::select(n_tot) %>% unlist %>%  mean(na.rm = TRUE) %>% signif(2) %>% format(scientific = TRUE)` $\pm$ `r dat %>% dplyr::select(n_tot) %>% unlist %>% sd %>% signif(2) %>% format(scientific = TRUE)` individuals m^-2^. Community mean body sizes exhibited a similar range  from `r dat %>% dplyr::select(mbar_n) %>% min %>% signif(2) %>% format(scientific = TRUE)` to `r dat %>% dplyr::select(mbar_n) %>% max %>% signif(2) %>% format(scientific = TRUE)` with an average community mean body size of `r dat %>% dplyr::select(mbar_n) %>% unlist %>% mean(na.rm = TRUE) %>% round(2)` $\pm$ `r dat %>% dplyr::select(mbar_n) %>% unlist %>% sd(na.rm = TRUE) %>% round(2)` mg dry mass individual^-1^. 

Total community biomass estimates ranged from `r dat_summ %>% dplyr::select(b_est) %>% min %>% magrittr::divide_by(1000) %>% round(2)` to `r dat_summ %>% dplyr::select(b_est) %>% max %>% magrittr::divide_by(1000) %>% round(2)` 

To explore drivers of over- or under-yielding, 

```{r N-Mn_met plot, fig.cap='Figure 1. The scaling of community abundances by community abundance-weighted metabolic mass across the NEON streams.'}

# # create label vector for scaled breaks. s 
# lntot_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$ln_tot) + mean(dat$ln_tot)),1), scientific = TRUE)
# 
# lmbar_n_met_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_n_met) + mean(dat$lmbar_n_met)),1), scientific = TRUE)
# 
# dat %>% 
#   group_by(site_id) %>% 
# data_grid(lmbar_n_met = seq_range(lmbar_n_met, n = 51)) %>%
#   add_epred_draws(NM_met_nwt, ndraws = 100, re_formula = NA) %>% 
#   dplyr::mutate(.epred = log(.epred)) %>% 
#   ggplot()+
#   # geom_line(data = NM_met_nwt_pred, aes(x = lmbar_n_met, y = pred), linewidth = 1.1, linetype = 'dotted', color = 'darkgrey')+
#   geom_point(data = dat, aes(x = lmbar_n_met, y = ln_tot_s, color = site_id))+
#   geom_line(aes(x = lmbar_n_met, y = .epred, group = .draw), alpha = 0.1)+
#   geom_smooth(data = dat, aes(x = lmbar_n_met, y = ln_tot_s), se = FALSE, method = 'gam')+
#   scale_color_viridis(discrete = TRUE)+
#   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(NA, NA), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+
#   scale_x_continuous(name = expression(log[10]*"("*bar(M^0.75)["abun-weighted"]*")"), limits = c(NA,NA), breaks = seq.int(-3,3, by = 1), labels = lmbar_n_met_s_labels)+
#   theme(legend.position = 'none')
```


<!-- ```{r N-Mn plot, fig.cap='Figure 1. The scaling of community abundances by community mean body size across the NEON streams. Transparent grey lines represent a random sample of posterior draws from a linear model (n = 100), while the dotted line represents the relationship predicted by theory, $N ~ \\overline{M^{-0.75}}$. The linear model was fit on centered and scaled data and axis back-transformed to the original scale. The inset shows the predicted site-specific relationships between community abundance and mean body size from the mixed-effects model.'} -->

<!-- # create label vector for scaled breaks. s  -->
<!-- # lntot_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$ln_tot) + mean(dat$ln_tot)),1), scientific = TRUE) -->

<!-- lmbar_n_met_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_n_met) + mean(dat$lmbar_n_met)),1), scientific = TRUE) -->

<!-- inset = dat %>% -->
<!--   group_by(site_id) %>%  -->
<!--   data_grid(lmbar_n_met_s = seq_range(lmbar_n_met_s, n = 51)) %>% -->
<!--   ungroup %>%  -->
<!--   mutate(pred = predict(NM_met_nwt, newdata = .,)[,1]) %>% # re.form = ~(1 + lmbar_n_met_s|site_id), allow.new.levels = TRUE)[,1]) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(data = NM_met_nwt_pred, aes(x = lmbar_n_met_s, y = pred), linewidth = 1.1, linetype = 'dotted', color = 'darkgrey')+ -->
<!--   geom_line(aes(x = lmbar_n_met_s, y = pred, group = site_id, color = site_id))+ -->
<!--   scale_color_viridis(discrete = TRUE, alpha = 0.8)+ -->
<!--   scale_fill_viridis(discrete = TRUE)+ -->
<!--   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3.5, 3.5), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M)["abun-weighted"]*")"), limits = c(-3,4.51), breaks = seq.int(-3,3, by = 1), labels = lmbar_n_met_s_labels)+ -->
<!-- theme(legend.position = 'none', -->
<!--         axis.title = element_blank(), -->
<!--         axis.text = element_blank(), -->
<!--         panel.border = element_rect(color = 'black', fill = 'transparent'), -->
<!--         panel.background = element_rect()) -->
<!-- ``` -->

<!-- ```{r N-Mb_met plot,fig.cap='Figure 2. The scaling of community abundances by community biomass-weighted body size across the NEON streams.'} -->
<!-- lmbar_b_met_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_b_met) + mean(dat$lmbar_b_met)),1), scientific = TRUE) -->

<!-- dat %>%  -->
<!-- data_grid(lmbar_b_met_s = seq_range(lmbar_b_met_s, n = 51)) %>% -->
<!--   add_epred_draws(NM_met_bwt, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(data = NM_met_bwt_pred, aes(x = lmbar_b_met_s, y = pred), linewidth = 1.1, linetype =   'dotted', color = 'darkgrey')+ -->
<!--   geom_point(data = dat, aes(x = lmbar_b_met_s, y = ln_tot_s, color = site_id))+ -->
<!--   geom_line(aes(x = lmbar_b_met_s, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_smooth(data = dat, aes(x = lmbar_b_met_s, y = ln_tot_s), se = FALSE, method = 'gam')+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3, 3), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M^0.75)["biomass-weighted"]*")"), limits = c(-3.5,3), breaks = seq.int(-3,3, by = 1), labels = lmbar_b_met_s_labels)+ -->
<!--   theme(legend.position = 'none') -->
<!-- ``` -->

<!-- ```{r N-Mb plot,fig.cap='Figure 2. The scaling of community abundances by community biomass-weighted body size across the NEON streams.'} -->
<!-- lmbar_b_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_b) + mean(dat$lmbar_b)),1), scientific = TRUE) -->

<!-- dat %>%  -->
<!-- data_grid(lmbar_n_s = seq_range(lmbar_n_met_s, n = 51)) %>% -->
<!--   add_epred_draws(NM_nwt, re_formula = NA, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(data = NM_bwt_pred, aes(x = lmbar_b_s, y = pred), linewidth = 1.1, linetype =   'dotted', color = 'darkgrey')+ -->
<!--   geom_point(data = dat, aes(x = lmbar_b_s, y = ln_tot_s, color = site_id))+ -->
<!--   geom_line(aes(x = lmbar_b_s, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_smooth(data = dat, aes(x = lmbar_b_s, y = ln_tot_s), se = FALSE, method = 'gam')+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3, 3), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M)["biomass-weighted"]*")"), limits = c(-3.5,3), breaks = seq.int(-3,3, by = 1), labels = lmbar_b_met_s_labels)+ -->
<!--   theme(legend.position = 'none') -->

<!-- ``` -->


<!-- ```{r met residual analysis} -->

<!-- NMbarN_met_res = residuals(NM_met_nwt) %>%  data.frame %>% dplyr::select(NMnwt_met_res = 'Estimate', NMnwt_met_2.5 = 'Q2.5', NMnwt_met_97.5 = 'Q97.5')  -->
<!-- NMbarB_met_res = residuals(NM_met_bwt) %>% data.frame %>% dplyr::select(NMbwt_met_res = 'Estimate', NMbwt_met_2.5 = 'Q2.5', NMbwt_met_97.5 = 'Q97.5')  -->

<!-- dat = dat %>% bind_cols(NMbarN_met_res) %>% bind_cols(NMbarB_met_res) %>% left_join(s_dat, by = "site_id") -->

<!-- output = capture.output(brm(bf(NMnwt_met_res~lambda_med),  -->
<!--                             data = dat, -->
<!--                             family = gaussian(link = 'identity'), -->
<!--                             iter = 1000, -->
<!--                             thin = 1, -->
<!--                             file_refit = 'on_change', -->
<!--                             file = here("data/models/NM_nwt_met_res"), -->
<!--                             chains = 4, cores = 4, -->
<!--                             seed = 1312 -->
<!--                             )) -->

<!-- NMnwt_met_res = readRDS(here("data/models/NM_nwt_met_res.rds")) -->

<!-- output = capture.output(brm(bf(NMbwt_met_res~lambda_med),  -->
<!--                             data = dat, -->
<!--                             family = gaussian(link = 'identity'), -->
<!--                             iter = 1000, -->
<!--                             thin = 1, -->
<!--                             file_refit = 'on_change', -->
<!--                             file = here("data/models/NM_bwt_met_res"), -->
<!--                             chains = 4, cores = 4, -->
<!--                             seed = 1312 -->
<!--                             )) -->

<!-- NMbwt_met_res = readRDS(here("data/models/NM_bwt_met_res.rds")) -->

<!-- isd_NMnwt_met_plot = dat %>%  -->
<!--   add_epred_draws(NMnwt_met_res, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_point(aes(x = lambda_med,y = NMnwt_met_res, color = site_id))+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   labs(subtitle = expression("N-"*bar(M^0.75)['abun-weighted']))+ -->
<!--   theme(legend.position = 'none', -->
<!--         axis.title.x = element_blank(), -->
<!--         axis.title.y = element_blank()) -->

<!-- isd_NMbwt_met_plot = dat %>%  -->
<!--   add_epred_draws(NMbwt_met_res, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_point(aes(y = NMbwt_met_res, x = lambda_med, color = site_id))+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   labs(subtitle = expression("N-"*bar(M^0.75)['biomass-weighted']))+ -->
<!--   theme(legend.position = 'none', -->
<!--         axis.title.x = element_blank(), -->
<!--         axis.title.y = element_blank()) -->

<!-- gridExtra::grid.arrange(isd_NMnwt_met_plot, isd_NMbwt_met_plot, ncol =2, -->
<!--                         bottom = expression(!Lamdba), -->
<!--                         left = expression(paste("\U03B5 (residuals from N")))#,bar(M^0.75), ")"))) -->

<!-- ``` -->


<!-- ```{r residual analysis, fig.cap="Figure X. The relationship between the individual size distribution rate parameter $\\lambda$ and residuals from the fitted cross community size relationship."} -->

<!-- NMbarN_res = residuals(NM_nwt) %>%  data.frame %>% dplyr::select(NMnwt_res = 'Estimate', NMnwt_2.5 = 'Q2.5', NMnwt_97.5 = 'Q97.5')  -->

<!-- dat = dat %>% bind_cols(NMbarN_res) %>% bind_cols(NMbarB_res) %>% left_join(s_dat, by = "site_id") -->

<!-- dat = dat %>% bind_cols(NMbarN_res)  -->

<!-- output = capture.output(brm(bf(NMnwt_res~lambda_med+(1+lambda_med|site_id)),  -->
<!--                             data = dat, -->
<!--                             family = gaussian(link = 'identity'), -->
<!--                             iter = 1000, -->
<!--                             thin = 1, -->
<!--                             file_refit = 'never', -->
<!--                             file = here("data/models/NM_nwt_res"), -->
<!--                             chains = 4, cores = 4, -->
<!--                             sample_prior = 'yes', -->
<!--                             save_pars = save_pars(all = TRUE), -->
<!--                             seed = 1312 -->
<!--                             )) -->

<!-- NMnwt_res = readRDS(here("data/models/NM_nwt_res.rds")) -->

<!-- isd_NMnwt_plot = dat %>%  -->
<!--   add_epred_draws(NMnwt_res, re_formula = NA, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_point(aes(x = lambda_med,y = NMnwt_res, color = site_id))+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   scale_x_continuous(name = expression(lambda))+ -->
<!--   labs(subtitle = expression("N-"*bar(M^0.75)['abun-weighted']))+ -->
<!--   theme(legend.position = 'none') -->

<!-- isd_NMnwt_plot -->

<!-- ``` -->


<!-- ```{r residual from theory, fig.cap = "Figure X. The relationship between the individual size distribution rate parameter $\\lambda$ and residuals from the theoretical cross community size relationship, $N ~ M^{-0.75}$. The size of each point is scaled to the mean body size of the community."} -->

<!-- output = capture.output(brm(bf(resid_theory~lambda_med+(1+lambda_med|site_id)),  -->
<!--                             data = NM_nwt_pred, -->
<!--                             family = gaussian(link = 'identity'), -->
<!--                             iter = 1000, -->
<!--                             thin = 1, -->
<!--                             file_refit = 'never', -->
<!--                             file = here("data/models/NM_nwt_theory"), -->
<!--                             chains = 4, cores = 4, -->
<!--                             sample_prior = 'yes', -->
<!--                             save_pars = save_pars(all = TRUE), -->
<!--                             seed = 1312 -->
<!--                             )) -->

<!-- NMnwt_res_theo = readRDS(here("data/models/NM_nwt_theory.rds")) -->

<!-- # NM_nwt_pred_out = NM_nwt_pred %>% filter(lambda_med > -1.35) -->
<!-- # output = capture.output(brm(bf(resid_theory~lambda_med+(1|site_id)),  -->
<!-- #                             data = NM_nwt_pred_out, -->
<!-- #                             family = gaussian(link = 'identity'), -->
<!-- #                             iter = 1000, -->
<!-- #                             thin = 1, -->
<!-- #                             file_refit = 'never', -->
<!-- #                             file = here("data/models/NM_nwt_theory_outlier"), -->
<!-- #                             chains = 4, cores = 4, -->
<!-- #                             seed = 1312 -->
<!-- #                             )) -->
<!-- #  -->
<!-- # NMnwt_res_theo_out = readRDS(here("data/models/NM_nwt_theory_outlier.rds")) -->

<!-- isd_NMnwt_plot = NM_nwt_pred %>%  -->
<!--   add_epred_draws(NMnwt_res_theo, re_formula = NA, ndraws = 100) %>%  -->
<!--   ggplot()+ -->
<!--   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!--   geom_point(data = NM_met_nwt_pred, aes(x = lambda_med, y = resid_theory,  fill = site_id, size = lmbar_n_met_s),color = 'black', shape = 21, alpha = 0.6)+ -->
<!--   scale_color_viridis(discrete = TRUE, alpha = 0.8)+ -->
<!--   scale_fill_viridis(discrete = TRUE, alpha = 0.6)+ -->
<!--   scale_y_continuous(name = 'resids')+ -->
<!--   scale_x_continuous(name = expression(lambda))+ -->
<!--   labs(subtitle = expression("N-"*bar(M^0.75)['abun-weighted']))+ -->
<!--   theme(legend.position = 'none') -->

<!-- isd_NMnwt_plot -->
<!-- ``` -->


<!-- ```{r slope plots} -->

<!-- effectDf = NMnwt_res %>%  -->
<!--   spread_draws(b_lambda_med) %>%  -->
<!--   mutate(model = 'NMnwt_res') %>%  -->
<!--   bind_rows(NMnwt_res_theo %>% spread_draws(b_lambda_med) %>% mutate(model = 'NMnwt_res_theo')) -->

<!-- effectDf %>%  -->
<!--   ggplot(aes(x = b_lambda_med, y = model, fill = after_stat(x > 0)))+ -->
<!--   stat_halfeye()+ -->
<!--   scale_x_continuous(name = expression(Beta*"("*lambda*")"))+ -->
<!--   geom_vline(aes(xintercept = 0), linetype = 'dotted', color = 'black')+ -->
<!--   scale_fill_manual(values = c('gray80', 'skyblue'))+ -->
<!--   theme(legend.position = 'none') -->

<!-- ``` -->


```{r env plots}

## relationships with temperature
# output = capture.output(brm(bf(ln_tot~1 + mat_s + I(mat_s^2)), 
#             data = dat,
#             family = gaussian(link = 'identity'),
#             iter = 1000,
#             thin = 1, 
#             file_refit = 'never',
#             file = here("data/models/N_mat_gam"),
#             chains = 4, cores = 4,
#             seed = 1312
#             ))
# 
# N_mat = readRDS(here("data/models/N_mat_gam.rds"))
# 
# dat %>% 
#   data_grid(mat_s = seq_range(mat_s, n = 51)) %>% 
#   add_epred_draws(N_mat, ndraws= 100) %>% 
#   ggplot()+
#   geom_line(aes(x = mat_s, y = .epred, group = .draw), alpha = .1)+
#   geom_point(data = dat, aes(x = mat_s, y = ln_tot, color = site_id), size = 2)+
#   scale_color_viridis(discrete = TRUE)+
#   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(3, 8), expand = c(0,0), breaks = seq.int(3,8, by = 2), labels = format(10^seq.int(3,8, by = 2), scientific = TRUE))+
#   scale_x_continuous(name = "mat_s")+
#   theme(legend.position = 'none')
# 
# output = capture.output(brm(bf(log10(b_m2)~1 + mat_s + I(mat_s^2)), 
#             data = dat,
#             family = gaussian(link = 'identity'),
#             iter = 1000,
#             thin = 1, 
#             file_refit = 'never',
#             file = here("data/models/B_mat_gam"),
#             chains = 4, cores = 4,
#             seed = 1312
#             ))
# 
# B_mat = readRDS(here("data/models/B_mat_gam.rds"))
# 
# dat %>% 
#   data_grid(mat_s = seq_range(mat_s, n = 51)) %>% 
#   add_epred_draws(B_mat, ndraws= 100) %>% 
#   ggplot()+
#   geom_line(aes(x = mat_s, y = .epred, group = .draw), alpha = .1)+
#   geom_point(data = dat, aes(x = mat_s, y = log10(b_m2), color = site_id), size = 2)+
#   scale_color_viridis(discrete = TRUE)+
#   scale_y_continuous(name = expression(log[10]*"(B)"), limits = c(2, 6), expand = c(0,0), breaks = seq.int(2,6, by = 2), labels = format(10^seq.int(2,6, by = 2), scientific = TRUE))+
#   scale_x_continuous(name = "mat_s")+
#   theme(legend.position = 'none')
```

```{r isd-ccsr}
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = ))

```

```{r N and B models}

# ## relationships with gpp
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_gpp_s, y = ln_tot))+
#   geom_smooth(aes(x = log_gpp_s, y = ln_tot), se = FALSE)
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_gpp_s, y = log10(b_m2)))+
#   geom_smooth(aes(x = log_gpp_s, y = log10(b_m2)), se = FALSE)
# 
# ## relationship with om
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_om_s, y = ln_tot))+
#   geom_smooth(aes(x = log_om_s, y = ln_tot), se = FALSE)
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_om_s, y = log10(b_m2)))+
#   geom_smooth(aes(x = log_om_s, y = log10(b_m2)), se = FALSE)
# 
# # relationship of Mbar with mat
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = mat_s, y = lmbar_n))+
#   geom_smooth(aes(x = mat_s, y = lmbar_n), se=FALSE)
# 
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = mat_s, y = lmbar_b))+
#   geom_smooth(aes(x = mat_s, y = lmbar_b), se=FALSE)
# 
# # relationship of Mbar with mat
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_gpp_s, y = lmbar_n))+
#   geom_smooth(aes( x = log_gpp_s, y = lmbar_n), se = FALSE)
# 
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_gpp_s, y = lmbar_b))+
#   geom_smooth(aes(x = log_gpp_s, y = lmbar_b), se = FALSE)
# 
# # relationship of Mbar with mat
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_om_s, y = lmbar_n))+
#   geom_smooth(aes(x = log_om_s, y = lmbar_n), se = FALSE)
# 
# 
# dat %>% 
#   ggplot()+
#   geom_point(aes(x = log_om_s, y = lmbar_b))+
#   geom_smooth(aes(x = log_om_s, y = lmbar_b), se = FALSE)


```

# References

<div id="refs"></div>

\newpage

# Appendix 

## Body size treatment

While the calculation of total abundance is straightforward, estimating mean body size of the community can be done in multiple ways: 1) by taking the mean of all individuals (i.e., abundance-weighted mean), by calculating the relative biomass of each body size and using this to weight body size by relative biomass (i.e., biomass-weighted), and lastly to correct each mass to metabolic mass (*M*^0.75^) and take the abundance- or biomass-weighted mean of these corrected body sizes. The theorized relationship between abundance and body size in $N \propto M$ is based on energy use, i.e. metabolism, and metabolism scales non-linearly with body size, therefore, the metabolic correction is most appropriate [@white2007]. These differences can have significant influence on the community biomass estimates (Figure S1). 

## Pareto extrapolation

```{r pareto extrapolation}

output = 
  capture.output(
    brm(bf(ln_est ~lmbar_n_est_met + (1 + lmbar_n_est_met|site_id)),
        data = dat,
        family = gaussian(link = 'identity'),
        iter = 2000,
        thin = 1,
        file_refit = 'on_change',
        file = here("data/models/NM_est_met_nwt"),
        control = list(adapt_delta = 0.99),
        chains = 4, cores = 4,
        seed = 1312
        )
    )
NM_est_met_nwt = readRDS(here("data/models/NM_est_met_nwt.rds"))
NM_est_met_nwt_cond = conditional_effects(NM_est_met_nwt) %>% flatten %>% data.frame

output = 
  capture.output(
    brm(bf(ln_tot~lmbar_n_met + (1 + lmbar_n_met|site_id)),
        data = dat,
        family = gaussian(link = 'identity'),
        iter = 2000,
        thin = 1,
        file_refit = 'on_change',
        file = here("data/models/NM_met_nwt"),
        control = list(adapt_delta = 0.99),
        chains = 4, cores = 4,
        seed = 1312
        )
    )
NM_met_nwt = readRDS(here("data/models/NM_met_nwt.rds"))
NM_met_nwt_cond = conditional_effects(NM_met_nwt) %>% flatten %>% data.frame


NM_est_met_nwt_int = mean(c(min(dat$ln_est),max(dat$ln_tot)))
NM_est_met_nwt_theory = data.frame(lmbar_n_est_met = seq(min(dat$lmbar_n_est_met), max(dat$lmbar_n_met), length.out = 50)) %>%
  mutate(pred = NM_est_met_nwt_int + lmbar_n_est_met*-1)

M_breaks = log(c(0.001,0.01,0.1,1,10,100,1000,10000))
M_labels = exp(M_breaks)

N_breaks = seq.int(round(min(dat$ln_tot, na.rm = TRUE)), 33, by= 3)#round(max(dat$ln_tot, na.rm = TRUE)20), by = 3)
N_labels = c(format(exp(N_breaks[N_breaks <= 9]), scientific = FALSE, digits = 1), format(exp(N_breaks[N_breaks >9]), scientific = TRUE, digits = 2))

n_m_extrapolate_plot = 
dat %>% 
  ggplot()+
  geom_ribbon(data = NM_est_met_nwt_cond,aes(x = lmbar_n_est_met, ymin = lower__, ymax = upper__), fill = 'darkgreen', alpha = 0.5)+
  geom_ribbon(data = NM_met_nwt_cond,aes(x = lmbar_n_met, ymin = lower__, ymax = upper__), fill = 'grey', alpha = 0.5)+
  geom_line(data = NM_est_met_nwt_cond,aes(x = lmbar_n_est_met, y = estimate__), color = 'darkgreen', linewidth = 1)+
  geom_line(data = NM_met_nwt_cond,aes(x = lmbar_n_met, y = ln_tot), color = 'grey', linewidth = 1)+
  geom_line(data = NM_est_met_nwt_theory, aes(x = lmbar_n_est_met, y = pred))+
  geom_point(aes(x = lmbar_n_met, y = ln_tot, fill = site_id), color = 'grey', alpha = 0.5, shape = 21)+
  geom_point(aes(x = lmbar_n_met, y = ln_est, fill = site_id), color = 'grey', alpha = 0.5, shape = 22)+
  geom_point(data = dat %>% summarise(lmbar_n_est_met = mean(lmbar_n_est_met),
                                      ln_est = mean(ln_est),
                                      ,.by = 'site_id'),
             aes(x = lmbar_n_est_met, y = ln_est, fill = site_id), shape = 22, size = 3)+
  geom_point(data = dat %>% summarise(lmbar_n_met = mean(lmbar_n_met),
                                      ln_tot = mean(ln_tot), .by = 'site_id'), aes(x = lmbar_n_met, y = ln_tot, fill = site_id), shape = 21, size = 3)+
  scale_x_continuous(name = expression(~bar(M^0.75)~"(mg "*ind^-1*")"),
                     breaks = M_breaks,
                     labels = M_labels,
                     limits = c(-5.5,7.8))+
  scale_y_continuous(name = expression("Abundance (individuals    "~m^-2~")"),
                     breaks = N_breaks,
                     labels = N_labels,
                     limits = c(0,27))+
  scale_fill_viridis(discrete = TRUE)+
  guides(group = "none",
         fill = "none",
         color = "none")+
  scale_color_manual(breaks = c("Observed","Modeled"),
                     values = c("grey", "darkgreen"))+
  theme(legend.position = 'inside',
        legend.position.inside = c(0.5,0.5),
        legend.justification.inside = c(1,1));n_m_extrapolate_plot 
saveRDS(n_m_extrapolate_plot, here("doc/plots/nm_extrapolate_plot.rds"))
```

```{r NB met comparison}

dat %>% 
  ggplot()+
  geom_point(aes(x = lmbar_n_met, lmbar_b_met, color = site_id), size = 1.3)+
  scale_color_viridis(discrete = TRUE)+
  geom_abline()+
  scale_x_continuous(name = expression(log*"("*bar(M^0.75)["abun-weighted"]*")"))+
  scale_y_continuous(name = expression(log*"("*bar(M^0.75)["biomass-weighted"]*")"))+
  theme(legend.position = 'none')

```

<!-- ```{r N-B body size, fig.cap= 'Figure S1. The relationship between different measures of community mean body size. a) uncorrected mean body size weighted by abundance and biomass, b) mean abundance-weighted body mass vs abundance-weighted body mass with a metabolic correction, and c) biomass-weighted vs biomass-weighted with metabolic correction.' } -->

<!-- M_nbwt_plot = dat %>%  -->
<!--   ggplot()+ -->
<!--   geom_point(aes(x = lmbar_n, y = lmbar_b, color = site_id), size = 1.3)+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   geom_abline()+ -->
<!--   annotate('text', label = 'a)', x = -Inf, y = Inf, hjust = 0, vjust = 1)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M)["abun-weighted"]*")"))+ -->
<!--   scale_y_continuous(name = expression(log[10]*"("*bar(M)["biomass-weighted"]*")"))+ -->
<!--   theme(legend.position = 'none') -->

<!-- M_nwt_plot = dat %>%  -->
<!--   ggplot()+ -->
<!--   geom_point(aes(x = lmbar_n, y = lmbar_n0.75, color = site_id), size = 1.3, shape = 22)+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   geom_abline()+ -->
<!--   annotate('text', label = 'b)', x = -Inf, y = Inf, hjust = 0, vjust = 1)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M)["abun-weighted"]*")"))+ -->
<!--   scale_y_continuous(name = expression(log[10]*"("*bar(M^0.75)["abun-weighted"]*")"))+ -->
<!--   theme(legend.position = 'none') -->

<!-- M_bwt_plot = dat %>%  -->
<!--   ggplot()+ -->
<!--   geom_point(aes(x = lmbar_b, y = lmbar_b0.75, color = site_id), size = 1.3, shape = 23)+ -->
<!--   scale_color_viridis(discrete = TRUE)+ -->
<!--   geom_abline()+ -->
<!--   annotate('text', label = 'c)', x = -Inf, y = Inf, hjust = 0, vjust = 1)+ -->
<!--   scale_x_continuous(name = expression(log[10]*"("*bar(M)["biomass-weighted"]*")"))+ -->
<!--   scale_y_continuous(name = expression(log[10]*"("*bar(M^0.75)["biomass-weighted"]*")"))+ -->
<!--   theme(legend.position = 'none') -->

<!-- gridExtra::grid.arrange(grobs = list(as_grob(M_nbwt_plot),  -->
<!--                              as_grob(M_nwt_plot), -->
<!--                              as_grob(M_bwt_plot)), -->
<!--                         layout_matrix = rbind(c(1,1,1,1), -->
<!--                                               c(2,2,3,3)), nrow = 2) -->

<!-- ``` -->

<!-- # ```{r uncorrected models} -->
<!-- ## calculate the bayesian linear regression -->

<!-- # output = capture.output(brm(bf(ln_tot_s~lmbar_n_s), -->
<!-- #               data = dat, -->
<!-- #               family = gaussian(link = 'identity'), -->
<!-- #               iter = 1000, -->
<!-- #               thin = 1, -->
<!-- #               file_refit = 'never', -->
<!-- #               file = here("data/models/NM_nwt"), -->
<!-- #               sample_prior = 'yes', -->
<!-- #               chains = 4, cores = 4, -->
<!-- #               seed = 1312 -->
<!-- #               )) -->
<!-- #  -->
<!-- # NM_nwt = readRDS(here("data/models/NM_nwt.rds")) -->
<!-- # NM_nwt_int =fixef(NM_nwt)[1,'Estimate'] -->

<!-- # NM_nwt_pred = dat %>%  -->
<!-- #   data_grid(lmbar_n_s = lmbar_n_s) %>%  -->
<!-- #   mutate(pred = NM_nwt_int + lmbar_n_s*-1)%>%  -->
<!-- #   left_join(dat %>% dplyr::select(site_id, lmbar_n_s, ln_tot_s, lambda_med, log_gpp_s, log_om_s), by = 'lmbar_n_s') %>%  -->
<!-- #   mutate(resid_theory = ln_tot_s - pred) -->
<!-- ``` --> 

<!-- # ```{r met-corrected-bodysize-comparison} -->
<!-- #  -->
<!-- # dat %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_point(aes(x = lmbar_n_met, lmbar_n, color = site_id), size = 1.3)+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   geom_abline()+ -->
<!-- #   scale_x_continuous(name = expression(log[10]*"("*bar(M^0.75)["abun-weighted"]*")"))+ -->
<!-- #   scale_y_continuous(name = expression(log[10]*"("*bar(M)["abund-weighted"]*")"))+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- #  -->
<!-- # dat %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_point(aes(x = lmbar_b_met, lmbar_b, color = site_id), size = 1.3)+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   geom_abline()+ -->
<!-- #   scale_x_continuous(name = expression(log[10]*"("*bar(M^0.75)["biomass-weighted"]*")"))+ -->
<!-- #   scale_y_continuous(name = expression(log[10]*"("*bar(M)["biomass-weighted"]*")"))+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- #  -->
<!-- # ``` -->

<!-- # output = capture.output(brm(bf(ln_tot_s~lmbar_b_s), -->
<!-- #               data = dat, -->
<!-- #               family = gaussian(link = 'identity'), -->
<!-- #               iter = 1000, -->
<!-- #               thin = 1, -->
<!-- #               file_refit = 'never', -->
<!-- #               file = here("data/models/NM_bwt"), -->
<!-- #               sample_prior = 'yes', -->
<!-- #               chains = 4, cores = 4, -->
<!-- #               seed = 1312 -->
<!-- #               )) -->
<!-- # NM_bwt = readRDS(here("data/models/NM_bwt.rds")) -->
<!-- # NM_bwt_int =fixef(NM_bwt)[1,'Estimate'] -->
<!-- #  -->
<!-- # NM_bwt_pred = dat %>%  -->
<!-- #   data_grid(lmbar_b_s = lmbar_b_s) %>% -->
<!-- #   mutate(pred = NM_bwt_int + lmbar_b_s*-1) %>%  -->
<!-- #   left_join(dat %>% dplyr::select( site_id, lmbar_b_s, ln_tot_s, lambda_med, log_gpp_s,log_om_s), by = 'lmbar_b_s') %>%  -->
<!-- #   mutate(resid_theory = ln_tot_s - pred) -->

<!-- ```{r N-Mn uncorrected plot, fig.cap='Figure S2. The scaling of community abundances by community abundance-weighted body size across the NEON streams.'} -->

<!-- # create label vector for scaled breaks. s  -->
<!-- lntot_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$ln_tot) + mean(dat$ln_tot)),1), scientific = TRUE) -->

<!-- lmbar_n_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_n) + mean(dat$lmbar_n)),1), scientific = TRUE) -->

<!-- # dat %>%  -->
<!-- # data_grid(lmbar_n_s = seq_range(lmbar_n_s, n = 51)) %>% -->
<!-- #   add_epred_draws(NM_nwt, ndraws = 100) %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_line(data = NM_nwt_pred, aes(x = lmbar_n_s, y = pred), linewidth = 1.1, linetype = 'dotted', color = 'darkgrey')+ -->
<!-- #   geom_point(data = dat, aes(x = lmbar_n_s, y = ln_tot_s, color = site_id))+ -->
<!-- #   geom_line(aes(x = lmbar_n_s, y = .epred, group = .draw), alpha = 0.1)+ -->
<!-- #   geom_smooth(data = dat, aes(x = lmbar_n_s, y = ln_tot_s), se = FALSE, method = 'gam')+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3.5, 3.5), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!-- #   scale_x_continuous(name = expression(log[10]*"("*bar(M)["abun-weighted"]*")"), limits = c(-3,4.51), breaks = seq.int(-3,3, by = 1), labels = lmbar_n_s_labels)+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- ``` -->

<!-- ```{r N-Mb uncorrected plot,fig.cap='Figure S3. The scaling of community abundances by community biomass-weighted body size across the NEON streams.'} -->
<!-- lmbar_b_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_b) + mean(dat$lmbar_b)),1), scientific = TRUE) -->

<!-- # dat %>%  -->
<!-- # data_grid(lmbar_b_s = seq_range(lmbar_b_s, n = 51)) %>% -->
<!-- #   add_epred_draws(NM_bwt, ndraws = 100) %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_line(data = NM_bwt_pred, aes(x = lmbar_b_s, y = pred), linewidth = 1.1, linetype =   'dotted', color = 'darkgrey')+ -->
<!-- #   geom_point(data = dat, aes(x = lmbar_b_s, y = ln_tot_s, color = site_id))+ -->
<!-- #   geom_line(aes(x = lmbar_b_s, y = .epred, group = .draw), alpha = 0.1)+ -->
<!-- #   geom_smooth(data = dat, aes(x = lmbar_b_s, y = ln_tot_s), se = FALSE, method = 'gam')+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3, 3), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!-- #   scale_x_continuous(name = expression(log[10]*"("*bar(M)["biomass-weighted"]*")"), limits = c(-3.5,3), breaks = seq.int(-3,3, by = 1), labels = lmbar_b_s_labels)+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- ``` -->

<!-- ```{r N-Mb plot2,fig.cap='Figure S4. The scaling of community abundances by community biomass-weighted body size across the NEON streams.The blue line represents a generalized additive model fit to the data. Transparent grey lines represent a random sample of posterior draws from a linear model (n = 100).'} -->

<!-- # output = capture.output(brm(bf(ln_tot_s~lmbar_b0.75_s), -->
<!-- #               data = dat, -->
<!-- #               family = gaussian(link = 'identity'), -->
<!-- #               iter = 1000, -->
<!-- #               thin = 1, -->
<!-- #               file_refit = 'never', -->
<!-- #               file = here("data/models/NM_bwt"), -->
<!-- #               chains = 4, cores = 4, -->
<!-- #               seed = 1312 -->
<!-- #               )) -->
<!-- #  -->
<!-- # NM_bwt = readRDS(here("data/models/NM_bwt.rds")) -->
<!-- # NM_bwt_int =fixef(NM_bwt)[1,'Estimate'] -->
<!-- #  -->
<!-- # NM_bwt_pred = dat %>%  -->
<!-- #   data_grid(lmbar_b0.75_s = lmbar_b0.75_s) %>% -->
<!-- #   mutate(pred = NM_bwt_int + lmbar_b0.75_s*-1) %>%  -->
<!-- #   left_join(dat %>% dplyr::select( site_id, lmbar_b0.75_s, ln_tot_s, lambda_med, log_gpp_s,log_om_s), by = 'lmbar_b0.75_s') %>%  -->
<!-- #   mutate(resid_theory = ln_tot_s - pred) -->
<!-- #  -->
<!-- # lmbar_b0.75_s_labels = format(signif(10^(seq.int(-3,3)*sd(dat$lmbar_b0.75) + mean(dat$lmbar_b0.75)),1), scientific = TRUE) -->
<!-- #  -->
<!-- # dat %>%  -->
<!-- # data_grid(lmbar_b0.75_s = seq_range(lmbar_b0.75_s, n = 51)) %>% -->
<!-- #   add_epred_draws(NM_bwt, ndraws = 100) %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_line(data = NM_bwt_pred, aes(x = lmbar_b0.75_s, y = pred), linewidth = 1.1, linetype =   'dotted', color = 'darkgrey')+ -->
<!-- #   geom_point(data = dat, aes(x = lmbar_b0.75_s, y = ln_tot_s, color = site_id))+ -->
<!-- #   geom_line(aes(x = lmbar_b0.75_s, y = .epred, group = .draw), alpha = 0.1)+ -->
<!-- #   geom_smooth(data = dat, aes(x = lmbar_b0.75_s, y = ln_tot_s), se = FALSE, method = 'gam')+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   scale_y_continuous(name = expression(log[10]*"(N)"), limits = c(-3, 3), expand = c(0,0), breaks = seq.int(-3,3, by = 1), labels = lntot_s_labels)+ -->
<!-- #   scale_x_continuous(name = expression(log[10]*"("*bar(M^0.75)["biomass-weighted"]*")"), limits = c(-3.5,3), breaks = seq.int(-3,3, by = 1), labels = lmbar_b0.75_s_labels)+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- #  -->
<!-- # NMbarB_res = residuals(NM_bwt) %>% data.frame %>% dplyr::select(NMbwt_res = 'Estimate', NMbwt_2.5 = 'Q2.5', NMbwt_97.5 = 'Q97.5') -->
<!-- #  -->
<!-- # dat = dat %>% bind_cols(NMbarB_res) -->

<!-- ``` -->

<!-- ```{r biomass residual analysis} -->

<!-- # output = capture.output(brm(bf(NMbwt_res~lambda_med),  -->
<!-- #                             data = dat, -->
<!-- #                             family = gaussian(link = 'identity'), -->
<!-- #                             iter = 1000, -->
<!-- #                             thin = 1, -->
<!-- #                             file_refit = 'never', -->
<!-- #                             file = here("data/models/NM_bwt_res"), -->
<!-- #                             chains = 4, cores = 4, -->
<!-- #                             seed = 1312 -->
<!-- #                             )) -->
<!-- #  -->
<!-- # NMbwt_res = readRDS(here("data/models/NM_bwt_res.rds")) -->
<!-- #  -->
<!-- # isd_NMbwt_plot = dat %>%  -->
<!-- #   add_epred_draws(NMbwt_res, ndraws = 100) %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!-- #   geom_point(aes(y = NMbwt_res, x = lambda_med, color = site_id))+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   labs(subtitle = expression("N-"*bar(M^0.75)['biomass-weighted']))+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- #  -->
<!-- # isd_NMbwt_plot -->
<!-- ``` -->

<!-- ```{r biomass residuals from theory} -->

<!-- # output = capture.output(brm(bf(resid_theory~lambda_med+(1|site_id)),  -->
<!-- #                             data = NM_bwt_pred, -->
<!-- #                             family = gaussian(link = 'identity'), -->
<!-- #                             iter = 1000, -->
<!-- #                             thin = 1, -->
<!-- #                             file_refit = 'never', -->
<!-- #                             file = here("data/models/NM_bwt_theory"), -->
<!-- #                             chains = 4, cores = 4, -->
<!-- #                             seed = 1312 -->
<!-- #                             )) -->
<!-- # NMbwt_res_theo = readRDS(here("data/models/NM_bwt_theory.rds")) -->
<!-- #  -->
<!-- # isd_NMbwt_plot = NM_bwt_pred %>%  -->
<!-- #   add_epred_draws(NMbwt_res_theo, re_formula = NA,ndraws = 100) %>%  -->
<!-- #   ggplot()+ -->
<!-- #   geom_line(aes(x = lambda_med, y = .epred, group = .draw), alpha = 0.1)+ -->
<!-- #   geom_point(aes(y = resid_theory, x = lambda_med, color = site_id))+ -->
<!-- #   scale_color_viridis(discrete = TRUE)+ -->
<!-- #   labs(subtitle = expression("N-"*M['biomass-weighted']))+ -->
<!-- #   theme(legend.position = 'none') -->
<!-- #  -->
<!-- # isd_NMbwt_plot -->

<!-- ``` -->
